---
title: "LClinton Doing Data Science Homework 3"
author: "Laurence Clinton"
date: "January 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### QUESTION 1


##### Laurence@Faith MINGW64 /d/SMU/DataScience_Course
##### $ mkdir gitwkspace

##### Laurence@Faith MINGW64 /d/SMU/DataScience_Course
##### $ cd gitwkspace/

##### Laurence@Faith MINGW64 
##### /d/SMU/DataScience_Course/gitwkspace
##### $ pwd
##### /d/SMU/DataScience_Course/gitwkspace

##### Laurence@Faith MINGW64 ## /d/SMU/DataScience_Course/gitwkspace
##### $ git init
##### Initialized empty Git repository in 
##### D:/SMU/DataScience_Course/gitwkspace/.git/

##### Laurence@Faith MINGW64 
##### /d/SMU/DataScience_Course/gitwkspace (master)
##### $ git clone https://github.com/awesomedata/awesome-public-datasets.git

---
Cloning into 'awesome-public-datasets'...
remote: Enumerating objects: 76, done.
remote: Counting objects: 100% (76/76), done.
remote: Compressing objects: 100% (37/37), done.
remote: Total 1692 (delta 49), reused 66 (delta 39), pack-reused 1616
Receiving objects: 100% (1692/1692), 627.23 KiB | 1.69 MiB/s, done.
Resolving deltas: 100% (1003/1003), done.
---

### QUESTION 2A

#### setwd("D:/SMU/DataScience_Course/gitwkspace/awesome-public-datasets/Datasets")

#### df <- read.csv("D:/SMU/DataScience_Course/gitwkspace/awesome-public-datasets/Datasets/titanic.csv")

### QUESTION 2B

```{r working with datasets, echo=FALSE}
setwd("D:/SMU/DataScience_Course/gitwkspace/awesome-public-datasets/Datasets")

df <- read.csv("D:/SMU/DataScience_Course/gitwkspace/awesome-public-datasets/Datasets/titanic.csv")

msum <- sum(df$Sex=="male")

## 577

fsum <-sum(df$Sex=="female")

## 314
tsumm <- msum + fsum

fplot <- plot(x=fsum, y=tsumm, main="Frequency of Females",xlab="Females",ylab="Total Count")

```

```{r more datasets, echo=FALSE}
msum <- sum(df$Sex=="male")

## 577

fsum <-sum(df$Sex=="female")

## 314
tsumm <- msum + fsum
mplot <- plot(x=msum, y=tsumm, main="Frequency of Males",xlab="Males",ylab="Total Count")

```

### QUESTION 2C (Working with apply)

##### tapply(df$Fare,df$Survived,mean)
#####       0        1 
##### 22.11789 48.39541 

##### tapply(df$Survived,df$Sex,mean)
#####   female      male 
##### 0.7420382 0.1889081 

##### AgeWO_NA <- na.omit(df$Age)

##### mean(AgeWO_NA)
##### [1] 29.69912
 

### QUESTION 3: Function building

#### data <- read.csv("D:/SMU/DataScience_Course/gitwkspace/sleep/sleep_data_01.csv")

#### sleep_function <- function(data){
  
####    MedianAge <- median(data$Age,na.rm = TRUE)

####    MinDurSleep <- min(data$Duration, na.rm = TRUE)

####    MaxDurSleep <- max(data$Duration,na.rm = TRUE)

####    MeanRSES <- mean(data$RSES, na.rm = TRUE)

####    SdRSES <- sd(data$RSES, na.rm = TRUE)

####    MinDurSleep <- min(data$Duration, na.rm = TRUE)

####    MaxDurSleep <- max(data$Duration,na.rm = TRUE)

####    RangeDuration <- MaxDurSleep-MinDurSleep
  
####  report <- data.frame((MedianAge/5),(MeanRSES/5),(SdRSES/5),(RangeDuration))	

####  library(plyr)

####  report <- rename(report, c("X.MedianAge.5."="MedianAge","X.MeanRSES.5."="SelfEsteem","X.SdRSES.5."="SE_SD","X.RangeDuration."="DurationRange"))

####  #round report to 2 digits

####  report <- round(report, digits = 2)

####  return (report)
  
#### }

#### sleep_function(data)

```{r sleep, echo=FALSE}
#setwd("D:/SMU/DataScience_Course/gitwkspace")
data <- read.csv("D:/SMU/DataScience_Course/gitwkspace/sleep/sleep_data_01.csv")

sleep_function <- function(data){
  
  MedianAge <- median(data$Age,na.rm = TRUE)
  MinDurSleep <- min(data$Duration, na.rm = TRUE)
  MaxDurSleep <- max(data$Duration,na.rm = TRUE)
  MeanRSES <- mean(data$RSES, na.rm = TRUE)
  SdRSES <- sd(data$RSES, na.rm = TRUE)
  MinDurSleep <- min(data$Duration, na.rm = TRUE)
  MaxDurSleep <- max(data$Duration,na.rm = TRUE)
  RangeDuration <- MaxDurSleep-MinDurSleep
  
  report <- data.frame((MedianAge/5),(MeanRSES/5),(SdRSES/5),(RangeDuration))	
  library(plyr)
  report <- rename(report, c("X.MedianAge.5."="MedianAge", "X.MeanRSES.5."="SelfEsteem","X.SdRSES.5."="SE_SD","X.RangeDuration."="DurationRange"))
  #round report to 2 digits
  report <- round(report, digits = 2)
  return (report)
  
}

sleep_function(data)
```

### QUESTION 4


##### install.packages("remotes")
##### remotes::install_github("rudeboybert/fivethirtyeight", build_vignettes = TRUE)

##### library(fivethirtyeight)
##### data(package = "fivethirtyeight")

##### df <-data.frame(college_recent_grads)

##### vignette("fivethirtyeight", package = "fivethirtyeight")
 
#### URL info

##### https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/ 

##### dim(df)
##### [1] 173  21

##### colnames(df)
##### [1] "rank"                        "major_code"                 
##### [3] "major"                       "major_category"             
##### [5] "total"                       "sample_size"                
##### [7] "men"                         "women"                      
##### [9] "sharewomen"                  "employed"                   
##### [11] "employed_fulltime"           "employed_parttime"          
##### [13] "employed_fulltime_yearround" "unemployed"                 
##### [15] "unemployment_rate"           "p25th"                      
##### [17] "median"                      "p75th"                      
##### [19] "college_jobs"                "non_college_jobs"           
##### [21] "low_wage_jobs"              

##### URL: https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/

### QUESTION 5a and 5b

##### colnames(df)
##### [1] "rank"                        "major_code"                 
##### 1 [3] "major"                       "major_category"             
##### [5] "total"                       "sample_size"                
##### [7] "men"                         "women"                      
##### [9] "sharewomen"                  "employed"                   
##### [11] "employed_fulltime"           "employed_parttime"          
##### [13] "employed_fulltime_yearround" "unemployed"                 
##### [15] "unemployment_rate"           "p25th"                      
##### [17] "median"                      "p75th"                      
##### [19] "college_jobs"                "non_college_jobs"           
##### [21] "low_wage_jobs"   

##### ncol(df)
##### [1] 21


### QUESTION 5b 



##### major_count <- count(df$major_category)

##### major_count
                                     x freq
##### 1      Agriculture & Natural Resources   10
##### 2                                 Arts    8
##### 3               Biology & Life Science   14
##### 4                             Business   13
##### 5          Communications & Journalism    4
##### 6              Computers & Mathematics   11
##### 7                            Education   16
##### 8                          Engineering   29
##### 9                               Health   12
##### 10           Humanities & Liberal Arts   15
##### 11 Industrial Arts & Consumer Services    7
##### 12                   Interdisciplinary    1
##### 13                 Law & Public Policy    5
##### 14                   Physical Sciences   10
##### 15            Psychology & Social Work    9
##### 16                      Social Science    9



### QUESTION 5c


```{r fivethirtyeight, echo=FALSE}

remotes::install_github("rudeboybert/fivethirtyeight", build_vignettes = TRUE)

library(fivethirtyeight)
data(package = "fivethirtyeight")

df <-data.frame(college_recent_grads)

major_count <- count(df$major_category)

barplot(major_count$freq,names=major_count$x,main="Recent College Graduates By Major",xlab="Count",ylab="College Major",horiz=TRUE,col=c("Red"),las=1)

```

### QUESTION 5D

##### write.csv(df,file="fivethirtyeight.csv",row.names = FALSE)


### QUESTION 6


##### https://github.com/lpclinton/DDScienceHmk.git



